 

### 2021-06-22 vertical-thermal-review.Rmd
switched order of Tair and CO2/RH
this is to match order in figure 2.
also, the last paragraph refers most to Tair, so this improves the continuity

@@

**Relative humidity, $RH$, is generally highest in the understory and decreases with height across the vertical profile [Fig. `r fig_NEON_vertical`; e.g., @mcgregor_tree_nodate].**
Dense-canopy forests maintain higher daily maximum $RH$ below-canopy than open forests and nearby open areas, and this effect is greater in wetter conditions, and warmer months [@vonarxSpatiotemporalEffectsForest2012a]. 
In combination with $T_{air}$, $RH$ determines vapor pressure deficit ($VPD$) -- the driving force of water loss from a leaf, which tends to be greater in upper-canopy and canopy gaps than in the understory [@fauset_differences_2018; @tymenQuantifyingMicroenvironmentalVariation2017; @niinemetsPhotosyntheticAcclimationSimultaneous2004b]. Additionally, increase in canopy height and LAI contributes to lowering maximum $T_{air}$ and VPD in the understory [@juckerCanopyStructureTopography2018]. *( This last sentence needs work.)*

**Atmospheric carbon dioxide (CO~2~) concentrations tend to be higher near ground level at night, but largely dissipate during the day [@koike_leaf_2001; @yang_spatial_1999].** 
Given that differences are small during the day when photosynthesis is occurring, and that even nighttime differences are modest at the height of understory tree crowns, CO~2~ concentrations are unlikely to have much of an effect on the energy balance and metabolism of leaves across the forest vertical gradient.

>>>>

**Atmospheric concentrations carbon dioxide (CO~2~) and water vapor can also vary across the vertical gradient.**
Atmospheric CO~2~ concentrations tend to be higher near ground level at night, but largely dissipate during the day [@koike_leaf_2001; @yang_spatial_1999].
Given that differences are small during the day when photosynthesis is occurring, and that even nighttime differences are modest at the height of understory tree crowns, CO~2~ concentrations are unlikely to have much of an effect on the energy balance and metabolism of leaves across the forest vertical gradient.

Relative humidity, $RH$, tends to be higher in the understory and decrease with height across the vertical profile, although this trend is absent in open forests [Figs. `r fig_NEON_vertical`f, `r SIfig_NEON_all`, e.g., @mcgregor_tree_nodate].
Dense-canopy forests maintain higher daily maximum $RH$ below-canopy than open forests and nearby open areas, and this effect is greater in wetter conditions, and warmer months [@vonarxSpatiotemporalEffectsForest2012a]. 
In combination with $T_{air}$, $RH$ determines vapor pressure deficit ($VPD$) -- the driving force of water loss from a leaf, which tends to be greater in upper-canopy and canopy gaps than in the understory [@fauset_differences_2018; @tymenQuantifyingMicroenvironmentalVariation2017; @niinemetsPhotosyntheticAcclimationSimultaneous2004b]. Additionally, increase in canopy height and LAI contributes to lowering maximum $T_{air}$ and VPD in the understory [@juckerCanopyStructureTopography2018]. *( This last sentence needs work.)*

@@
